Pilot data analysis

### 2021-04-02 data_analysis_brms_updated.Rmd
Add method and results

```{r lmm1}
contrasts(exp1_data_to_include$Condition) <- c(-1,1)
contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

@@

lmm_acc_exp1 <- glmer(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt < 1500), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))

@@

blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

@@

>>>>

```{r lmm1}
contrasts(exp1_data_to_include$Condition) <- c(-1,1)
contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (Condition*PrimeDuration|source) + (Condition*PrimeDuration|Target))

@@

lmm_acc_exp1 <- glmer(data = exp1_data_to_include %>% filter(rt > 250 & corr != -1 & StimulusType == "Word" & rt < 2000), corr ~ Condition * PrimeDuration + (1|Target), family = binomial(link = "logit"))

@@

blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

blmm_exp1_rt_string <- make_stancode(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

@@

blmm_exp1_acc_string <- make_stancode(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "Word" & rt > 250 & rt < 2000), 
                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                 warmup = 1000,
                 iter = 5000,
                 chains = 4,
                 prior = prior_exp1,
                 family = bernoulli(link = "logit"),
                 inits = "random",
                 control = list(adapt_delta = 0.95),
                 cores = 4, backend = "cmdstanr", threads = threading(2))
